---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  eval = FALSE
)
```

# Analysis of Central Bank Speeches

> [!NOTE]
> This is a work in progress.

This repository documents the analysis of central bank speeches, obtained from
[Bank for International Settlements (BIS) Central Bankers' Speeches](https://www.bis.org/cbspeeches/index.htm?m=60).
The rendered documentation files can be viewed [here](https://adamoshen.github.io/cbspeeches/).

## Installing dependencies

First download or clone this repository and then activate the .Rproj file.

To install all dependencies required to replicate the analysis:

```{r}
# install.packages("pak")
pak::local_install_deps()
```

To install all dependencies required to replicate the analysis and compile documentation:

```{r}
# install.packages("pak")
pak::local_install_dev_deps()
```

## Data stats

[TODO]
