```{r, include=FALSE}
knitr::opts_chunk$set(eval = FALSE)
```

# Identifying the country from the text

This chapter documents the extraction of the institution giving the speech. Where applicable, the
country associated to the institution can then be identified.

## Initialisation

```{r}
library(tidyverse)
library(readxl)
library(pins)
library(pinsqs)
library(cld2)
library(AzureStor)

source(here::here("R", "azure_init.R"))

speeches_board <- storage_endpoint("https://cbspeeches1.dfs.core.windows.net/", token=token) %>%
  storage_container(name = "cbspeeches") %>%
  board_azure(path = "data-speeches")
```

## Load the data

```{r}
speeches <- speeches_board %>%
  pin_qread("speeches-raw")
```

## Perform language detection

Speeches where the dominant language is not English, were removed. Of the 18,827 speeches, 18,813
(99.93%) were English and 14 (0.7%) were not English.

```{r}
speeches <- speeches %>%
  mutate(lang_cld2 = detect_language(text)) %>%
  filter(lang_cld2 == "en") %>%
  select(-lang_cld2)
```

## Get country

The identification of speech countries can be briefly summarised as follows:

1. Extract institution name by regex patterns.
2. If unable to extract anything, or if the extracted institution is incorrect, the affiliation of
the author is manually identified by Google-ing.
3. Normalise central bank names according to the [format listed](https://www.bis.org/cbanks.htm) on
the BIS website.
4. Using the same list, identify the country from the bank name.

::: {.rmdnote}

This method was chosen instead of looking for mentions of country names in the first sentence of a
speech as there are many instances of the meeting location being a different country from the
affiliation of the author.

:::

### Extract institution by regex patterns

The institutions/organizations were extracted by looking for the general pattern of:
`[position] (of|of the) [institution name]` within the first sentence of each speech. An attempt at
the extraction of institution/organization is as follows:

```{r}
extract_pattern1 <- "(?<=(?:Board of Governors|Governing Board|Executive Board|Chief Executive Officer) of the )[^[:punct:]]+"
extract_pattern2 <- "(?<=(?:Governor|President|Chairman|Director|Executive|Manager|Directorate) of the )[^[:punct:]]+"
extract_pattern3 <- "(?<=Governor of )[^[:punct:]]+" # for Philippines
extract_pattern4 <- "(?:Central|Reserve) Bank of (?:[:upper:][:lower:]+\\s?)+"
extract_pattern5 <- "Bank of (?:[:upper:][:lower:]+\\s?)+"
extract_pattern6 <- "(?i)National Bank of Serbia|Swiss National Bank|Hong Kong Monetary Authority|Monetary Authority of Singapore|Banco de Espana|Banco de Portugal|Banco de Mexico|South African Reserve Bank|Sveriges Riksbank|Oesterreichische Nationalbank"
extract_pattern7 <- "Federal Reserve System"
extract_pattern8 <- "(?i)Bank of [:alpha:]+"

speeches <- speeches %>%
  mutate(
    # Remove periods after salutations, initials, and credentials
    text = str_remove_all(text, "(?<=Mr|Ms|Mrs|PhD|Dr|Dott|Prof|Jr|Sig|\\bp|\\bm|\\ba|\\bh|\\bc|\\bmult|vs|[A-Z0-9])\\."),
    text = str_replace_all(text, "Member Board of Governors", "Member of the Board of Governors"),
    text = str_replace_all(text, "Govenor", "Governor"),
    # Extract first sentence before looking for patterns.
    first_sentence = str_extract(text, "^[^.]+\\."),
    institution = str_extract(first_sentence, extract_pattern1),
    institution = if_else(is.na(institution), str_extract(first_sentence, extract_pattern2), institution),
    institution = if_else(is.na(institution), str_extract(first_sentence, extract_pattern3), institution),
    institution = if_else(is.na(institution), str_extract(first_sentence, extract_pattern4), institution),
    institution = if_else(institution == "People", "The People's Bank of China", institution),
    institution = if_else(is.na(institution), str_extract(first_sentence, extract_pattern5), institution),
    institution = if_else(is.na(institution), str_extract(first_sentence, extract_pattern6), institution),
    institution = if_else(is.na(institution), str_extract(first_sentence, extract_pattern7), institution),
    institution = if_else(is.na(institution), str_extract(first_sentence, extract_pattern8), institution)
  )
```

### Fill missing/incorrect institutions

Where extraction failed or was incorrect (determined by looking for `institution` values of `NA`
and values with low frequencies), the speeches' institutions/organizations were
manually determined by Google-ing the author or the speech. This information was stored in
`inst/data-misc/author_affiliations.csv`. The data was updated according to this spreadsheet (where
applicable).

```{r}
author_affiliations <- read_csv(here::here("inst", "data-misc", "author_affiliations.csv"))

speeches <- speeches %>%
  rows_update(author_affiliations, by="author")
```

Two speeches remained with missing values for author and institution. These missing values were
filled in as follows:

```{r}
missing_info <- tribble(
  ~doc, ~author, ~institution,
  "r180725i", "Pablo Hernandez de Cos", "Bank of Spain",
  "r180810b", "Jorgovanka Tabakovic", "National Bank of Serbia"
)

speeches <- speeches %>%
  rows_update(missing_info, by="doc")
```

### Normalise institution names

The [list of banks and their official names](https://www.bis.org/cbanks.htm) from the BIS website
were downloaded and stored in `inst/data-misc/bank_list.csv`. The extracted institution names from
the previous step are normalised to match the names in this list. Additional organizations were
added, such as BIS (Bank for International Settlements) and ECB (European Central Bank). All US
Federal Reserves were associated with the common bank name of `Federal Reserve Bank`.

::: {.rmdwarning}

From the regex patterns below, one may notice that some institution names contain typos, extracted
directly from the speech text. Examples include Italy as *Italty* and Latvia as *Lativa*. This may
be important to keep in mind when cleaning the text at a later step.

:::

```{r}
speeches <- speeches %>%
  mutate(
    institution = str_squish(institution),
    institution = case_when(
      str_detect(institution, "Federal Reserve|Atlanta|Chicago|Kansas City|New York|Saint Louis|San Francisco|America|BANK of NEW") ~ "Federal Reserve Bank",
      str_detect(institution, "European Central Bank") ~ "European Central Bank",
      str_detect(institution, "ECB") ~ "European Central Bank",
      str_detect(institution, "Mauritius") ~ "Bank of Mauritius",
      str_detect(institution, "Bundesbank") ~ "Deutsche Bundesbank",
      str_detect(institution, "Italy|Italty") ~ "Bank of Italy",
      str_detect(institution, "France") ~ "Bank of France",
      str_detect(institution, "Japan") ~ "Bank of Japan",
      str_detect(institution, "Korea") ~ "Bank of Korea",
      str_detect(institution, "Bank of Papua New Guinea") ~ "Bank of Papua New Guinea",
      str_detect(institution, "Bank of PNG") ~ "Bank of Papua New Guinea",
      str_detect(institution, "(?i)Mexico") ~ "Bank of Mexico",
      str_detect(institution, "China") ~ "The People's Bank of China",
      str_detect(institution, "Ireland") ~ "Central Bank of Ireland",
      str_detect(institution, "(?i)Portugal") ~ "Banco de Portugal",
      str_detect(institution, "Bosnia|Herzegovina") ~ "Central Bank of Bosnia and Herzegovina",
      str_detect(institution, "Romania") ~ "National Bank of Romania",
      str_detect(institution, "Malaysia") ~ "Central Bank of Malaysia",
      str_detect(institution, "Sierra Leone") ~ "Bank of Sierra Leone",
      str_detect(institution, "Thailand") ~ "Bank of Thailand",
      str_detect(institution, "(?i)Uganda") ~ "Bank of Uganda",
      str_detect(institution, "Slovenia") ~ "Bank of Slovenia",
      str_detect(institution, "Banka Slovenije") ~ "Bank of Slovenia",
      str_detect(institution, "Bangko|Philippine|\\bBSP\\b") ~ "Central Bank of the Philippines (Bangko Sentral ng Pilipinas)",
      str_detect(institution, "(?i)Riksbank") ~ "Sveriges Riksbank",
      str_detect(institution, "Sweden|Swedish") ~ "Sveriges Riksbank",
      str_detect(institution, "Riskbank|Risksbank") ~ "Sveriges Riksbank",
      str_detect(institution, "Swiss") ~ "Swiss National Bank",
      str_detect(institution, "Austria|Oesterreichische") ~ "Oesterreichische Nationalbank, the Austrian Central Bank",
      str_detect(institution, "Norges|Norwegian") ~ "Central Bank of Norway",
      str_detect(institution, "Denmark|Danmarks") ~ "Danmarks Nationalbank",
      str_detect(institution, "Nederlandsche|Netherlands|Nederlandse") ~ "De Nederlandsche Bank",
      str_detect(institution, "Macedonia") ~ "National Bank of the Republic of North Macedonia",
      str_detect(institution, "Spain") ~ "Bank of Spain",
      str_detect(institution, "Espana") ~ "Bank of Spain",
      str_detect(institution, "(?i)Canada") ~ "Bank of Canada",
      str_detect(institution, "(?i)Serbia") ~ "National Bank of Serbia",
      str_detect(institution, "Hong Kong") ~ "Hong Kong Monetary Authority",
      str_detect(institution, "India") ~ "Reserve Bank of India",
      str_detect(institution, "Bangladesh") ~ "Bangladesh Bank",
      str_detect(institution, "Indonesia") ~ "Bank Indonesia",
      str_detect(institution, "Algeria") ~ "Bank of Algeria",
      str_detect(institution, "Pakistan") ~ "State Bank of Pakistan",
      str_detect(institution, "England") ~ "Bank of England",
      str_detect(institution, "Finland") ~ "Bank of Finland",
      str_detect(institution, "Suomen Pankki") ~ "Bank of Finland",
      str_detect(institution, "(?i)Australia") ~ "Reserve Bank of Australia",
      str_detect(institution, "Bahrain") ~ "Central Bank of Bahrain",
      str_detect(institution, "Barbados") ~ "Central Bank of Barbados",
      str_detect(institution, "Bahamas") ~ "Central Bank of The Bahamas",
      str_detect(institution, "Belgium") ~ "National Bank of Belgium",
      str_detect(institution, "(?i)Botswana") ~ "Bank of Botswana",
      str_detect(institution, "Carribean") ~ "Eastern Caribbean Central Bank",
      str_detect(institution, "(?i)Cambodia") ~ "National Bank of Cambodia",
      str_detect(institution, "Chile") ~ "Central Bank of Chile",
      str_detect(institution, "Columbia") ~ "Central Bank of Colombia",
      str_detect(institution, "Croatia|Croation") ~ "Croatian National Bank",
      str_detect(institution, "Curacao") ~ "Central Bank of Curacao and Sint Maarten",
      str_detect(institution, "Cyprus") ~ "Central Bank of Cyprus",
      str_detect(institution, "Czech") ~ "Czech National Bank",
      str_detect(institution, "Ecuador") ~ "Central Bank of Ecuador",
      str_detect(institution, "Eesti Pank") ~ "Bank of Estonia",
      str_detect(institution, "(?i)Fiji") ~ "Reserve Bank of Fiji",
      str_detect(institution, "Gambia") ~ "Central Bank of The Gambia",
      str_detect(institution, "(?i)Ghana") ~ "Bank of Ghana",
      str_detect(institution, "Greece") ~ "Bank of Greece",
      str_detect(institution, "Guatemala") ~ "Bank of Guatemala",
      str_detect(institution, "Hellenic") ~ "Bank of Greece",
      str_detect(institution, "Iceland") ~ "Central Bank of Iceland",
      str_detect(institution, "Kenya") ~ "Central Bank of Kenya",
      str_detect(institution, "Kosovo") ~ "Central Bank of the Republic of Kosovo",
      str_detect(institution, "Kuwait") ~ "Central Bank of Kuwait",
      str_detect(institution, "Lativa") ~ "Bank of Latvia",
      str_detect(institution, "Lithuania") ~ "Bank of Lithuania",
      str_detect(institution, "Luxembourg") ~ "Central Bank of Luxembourg",
      str_detect(institution, "Malawi") ~ "Reserve Bank of Malawi",
      str_detect(institution, "Malta") ~ "Central Bank of Malta",
      str_detect(institution, "Mozambique") ~ "Bank of Mozambique",
      str_detect(institution, "Bank of Al\\b|Bank Al\\b|Al-Maghrib|Morocco") ~ "Bank Al-Maghrib (Central Bank of Morocco)",
      str_detect(institution, "Nepal") ~ "Central Bank of Nepal (Nepal Rastra Bank)",
      str_detect(institution, "New Zealand") ~ "Reserve Bank of New Zealand",
      str_detect(institution, "Poland|Polski") ~ "Narodowy Bank Polski",
      str_detect(institution, "Russia") ~ "Central Bank of the Russian Federation",
      str_detect(institution, "Saudi") ~ "Saudi Central Bank",
      str_detect(institution, "Seychelles") ~ "Central Bank of Seychelles",
      str_detect(institution, "Singapore") ~ "Monetary Authority of Singapore",
      str_detect(institution, "Slovakia|Slovenska") ~ "National Bank of Slovakia",
      str_detect(institution, "Solomon Islands") ~ "Central Bank of Solomon Islands",
      str_detect(institution, "South Africa") ~ "South African Reserve Bank",
      str_detect(institution, "Ceylon") ~ "Central Bank of Sri Lanka",
      str_detect(institution, "Swaziland|Eswatini") ~ "The Central Bank of Eswatini",
      str_detect(institution, "Trinidad") ~ "Central Bank of Trinidad and Tobago",
      str_detect(institution, "Tunisia") ~ "Central Bank of Tunisia",
      str_detect(institution, "Turkiye|Turkey") ~ "Central Bank of the Republic of Turkiye",
      str_detect(institution, "Emirates|UAE") ~ "Central Bank of the United Arab Emirates",
      str_detect(institution, "Ukraine") ~ "National Bank of Ukraine",
      str_detect(institution, "(?i)Zambia") ~ "Bank of Zambia",
      str_detect(institution, "Bank for International Settlements|\\bBIS\\b") ~ "Bank for International Settlements",
      str_detect(institution, "\\bBSC\\b") ~ "Banking Supervision Committee",
      str_detect(institution, "Basel") ~ "Basel Committee",
      .default = institution
    )
  )
```

### Get country from institution names

From the list of banks, we can associate each speech with a country by performing a join.

```{r}
bank_list <- read_csv(here::here("inst", "data-misc", "bank_list.csv"))

speeches <- speeches %>%
  left_join(bank_list, by="institution")
```

## Save the data

Writing the data to the pin board:

```{r}
speeches_board %>%
  pin_qsave(
    speeches,
    "speeches-with-country",
    title = "speeches with institutions and countries"
  )
```
