```{r, include=FALSE}
knitr::opts_chunk$set(eval = FALSE)
```

# Cleaning the BIS speeches

The cleaning of the BIS speeches is nearly identical to that of G7 and G10 as the text is quite
standard.

## Initialisation

```{r}
library(tidyverse)
library(pins)
library(pinsqs)
library(AzureStor)

source(here::here("R", "azure_init.R"))

speeches_board <- storage_endpoint("https://cbspeeches1.dfs.core.windows.net/", token=token) %>%
  storage_container(name = "cbspeeches") %>%
  board_azure(path = "data-speeches")
```

## Filter for BIS speeches

```{r}
speeches <- speeches_board %>%
  pin_qread("speeches-with-country") %>%
  filter(country == "Other_BIS")
```

## Repairs and removals

### Remove introductions

As before, the first sentence of each speech is only removed if a gratitude word is detected.
Otherwise, only the brief speech description is removed.

```{r}
speeches <- speeches %>%
  mutate(
    text = if_else(
      str_detect(first_sentence, pattern="(\\*\\s){3}"),
      if_else(
        str_detect(first_sentence, pattern="(?i)thank|acknowledge|honou?r|grateful|pleas|welcome|delight"),
        str_remove(text, pattern="^[^.]+\\."),
        str_remove(text, pattern="^.*(\\*\\s){3}")
      ),
      str_remove(text, pattern="^[^.]+\\.")
    ),
    text = str_squish(text)
  )
```

### Remove section headers

```{r}
speeches <- speeches %>%
  mutate(text = str_remove_all(text, "(Introduction|Closing remarks|Conclusion) (?=[:upper:])"))
```

### Remove references section

The references and concluding remarks can be removed using the `clean_general()` function.

```{r}
source(here::here("R", "clean_by_country.R"))

speeches <- speeches %>%
  mutate(text = clean_general(text))
```

### Miscellaneous removals

Mentions of "BIS central bankers' speeches" within speeches were removed.

```{r}
speeches <- speeches %>%
  mutate(text = str_remove_all(text, "(?i)BIS central bankers' speeches"))
```

### Remove mentions of own institution and country

It is of greater interest when a central bank mentions another central bank or another country.
Therefore, all self-mentions of the bank, country, and inhabitants were removed. For example, for
Canada, words to remove would include: Bank of Canada, BoC, Canada, Canada's, and Canadian. The
removal patterns corresponding to each bank are stored in
`inst/data-misc/bank_country_regex_patterns.csv`.

```{r}
bis_regex_pattern <- read_delim(
  here::here("inst", "data-misc", "bank_country_regex_patterns.csv"),
  delim = ",",
  escape_backslash = TRUE
) %>%
  filter(country == "Other_BIS") %>%
  pull(regex_pattern)

speeches <- speeches %>%
  mutate(text = str_remove_all(text, bis_regex_pattern))
```

## General cleaning

### Normalisation of COVID related terms

```{r}
speeches <- speeches %>%
  mutate(text = str_replace_all(text, "(?i)COVID|COVID19|COVID-19|coronavirus", "COVID"))
```

### Normalisation of select ngrams into acronyms

"Central Bank Digital Currency" is a particular 4-gram of interest and can be converted to its
abbreviated form.

```{r}
speeches <- speeches %>%
  mutate(text = str_replace_all(text, "(?i)Central Bank Digital Currency", "CBDC"))
```

### Remove non-ascii characters, emails, social media handles, and links

The only addition to this chunk of code is the last line, where links that do not begin with http,
https, or www, are removed, e.g. `google.ca`.

```{r}
speeches <- speeches %>%
  mutate(
    text = str_remove_all(text, "[:^ascii:]"),
    text = str_remove_all(text, "([[:alnum:]_.\\-]+)?@[[:alnum:].\\-]+"),
    text = str_remove_all(text, "https?://\\S+"),
    text = str_remove_all(text, "www\\.\\S+"),
    text = str_remove_all(text, "[A-Za-z]+\\.[A-Za-z]+(\\.[A-Za-z]+)*")
  )
```

### Remove/replace stray and/or excessive punctuation

A few minor changes here opting for the replacement of punctuation sequences with spaces, instead of
their removal.

```{r}
speeches <- speeches %>%
  mutate(
    text = str_remove_all(text, "(\\* )+"),
    text = str_replace_all(text, "\\?|!", "."),
    text = str_remove_all(text, ","),
    text = str_remove_all(text, "\""),
    text = str_replace_all(text, "'{2,}", "'"),
    text = str_remove_all(text, "\\B'(?=[:alpha:])"),
    text = str_remove_all(text, "(?<=[:alpha:])'\\B"),
    text = str_remove_all(text, "\\B'\\B"),
    text = str_replace_all(text, "\\.{3}", "."),
    text = str_replace_all(text, " \\. ", " "),
    text = str_replace_all(text, "-", " "),
    text = str_replace_all(text, "_", " "),
    text = str_remove_all(text, "\\(|\\)|\\{|\\}|\\[|\\]|\\||;|:|\\+")
  )
```

### Remove numerical quantities

References to figures, slides, and graphs were removed, in addition to dollar signs, percent signs,
and other numerical quantities.

```{r}
speeches <- speeches %>%
  mutate(
    text = str_remove_all(text, "\\$"),
    text = str_remove_all(text, "%"),
    text = str_remove_all(text, "[:digit:]+([.,]+[:digit:]+)*"),
    text = str_remove_all(text, "(Figure|Slide|Graph) [:digit:]+"),
    text = str_remove_all(text, "[:digit:]")
  )
```

### Remove excessive whitespace

Excessive whitespace resulting from previous replacements was removed.

```{r}
speeches <- speeches %>%
  mutate(text = str_squish(text))
```

### Remove unneeded columns

```{r}
speeches <- speeches %>%
  select(-first_sentence)
```

## Save the data

Writing the data to the pin board:

```{r}
speeches_board %>%
  pin_qsave(
    speeches,
    "speeches-bis-cleaned",
    title = "speeches for BIS, cleaned"
  )
```

Making a separate copy of the metadata as well:

```{r}
speeches_metadata <- speeches %>%
  select(doc, date, institution, country)

speeches_board %>%
  pin_qsave(
    speeches_metadata,
    "speeches-bis-metadata",
    title = "metadata for BIS speeches"
  )
```

