```{r, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, message=FALSE, warning=FALSE, fig.align="center")
```

# Explorations with NMF

The non-negative matrix factorization (NMF) files are currently stored under
`inst/NMFregress` ([GitHub](https://github.com/iamdavecampbell/NMFregress)). In this chapter, a
40-topic NMF model is fitted on the G7 speeches.

## Initialisation

```{r}
library(tidyverse)
library(pins)
library(pinsqs)
library(AzureStor)
library(ggiraph)

source(here::here("R", "azure_init.R"))

fs::dir_ls("inst/NMFregress", glob="*.R") %>%
  walk(source)

theme_set(theme_bw())
set_girafe_defaults(
  opts_toolbar = opts_toolbar(position="topright", saveaspng=FALSE),
  opts_zoom = opts_zoom(min=0.8, max=4)
)

speeches_board <- storage_endpoint("https://cbspeeches1.dfs.core.windows.net/", token=token) %>%
  storage_container(name = "cbspeeches") %>%
  board_azure(path = "data-speeches")

models_board <- storage_endpoint("https://cbspeeches1.dfs.core.windows.net/", token=token) %>%
  storage_container(name = "cbspeeches") %>%
  board_azure(path = "data-models")
```

Reading in the previously constructed term-document matrix:

```{r, eval=FALSE}
speeches <- speeches_board %>%
  pin_qread("speeches-g20-tdm")
```

## Model fitting

Custom anchors for particular topics of interest are supplied in the model fitting process. The
remaining anchors are determined by the model. Note that since the text in the term-document matrix
was lowercased and stemmed, supplied anchors also needed to be in their lowercased and stemmed form.

::: {.rmdnote}

The stemmed form of a word can be obtained by calling `SnowballC::wordstem("word")`.

:::

```{r, eval=FALSE}
nmf_input <- create_input(speeches, vocab=rownames(speeches), topics=40)

custom_anchors <- c("basel", "cbdc", "ukrain", "covid", "brexit")

nmf_output <- solve_nmf(nmf_input, user_anchors=custom_anchors)
```

Creating a checkpoint:

```{r, eval=FALSE}
models_board %>%
  pin_qsave(
    nmf_output,
    "nmf-g20-k=40",
    title = "40-topic nmf, g20, custom topics"
  )
```

## Explorations

Loading the required data:

```{r, echo=FALSE}
nmf_output <- local_board %>%
  pin_qread("nmf-g20-k=40", version="20250216T030104Z-21d5f")
```

```{r}
speeches_metadata <- local_board %>%
  pin_qread("speeches-g20-metadata")
```

### Pre-exploration data wrangling

::: {.rmdnote}

Variables that refer to `theta` pertain to the document-topic matrix.

:::

First, document-topic proportions were recovered from the NMF model.

```{r}
normalised_theta <- nmf_output %>%
  pluck("theta") %>%
  t() %>%
  magrittr::divide_by(rowSums(.)) %>%
  as_tibble(rownames = "doc") %>%
  pivot_longer(-doc, names_to="anchor", values_to="proportion")
```

Next, document-topic proportions were reunited with speech metadata. The document-topic proportions
were then aggregated and averaged by year-month to produce a monthly time series of topic
proportions.

```{r}
doc_dates <- speeches_metadata %>%
  select(doc, country, date)

theta_dates <- inner_join(normalised_theta, doc_dates, by="doc")

summarised_theta_by_month <- theta_dates %>%
  mutate(
    year = year(date),
    month = month(date)
  ) %>%
  group_by(country, year, month, anchor) %>%
  summarise(avg_proportion = mean(proportion, na.rm=TRUE)) %>%
  ungroup() %>%
  unite("date", year, month, sep="-") %>%
  mutate(date = ym(date)) %>%
  drop_na()
```

For plotting, rather than labelling a topic by its anchor word, a topic's top 10 words can be used
instead.

```{r}
label_top_words <- nmf_output %>%
  print_top_words() %>%
  map(str_flatten_comma) %>%
  list_c() %>%
  set_names(nmf_output$anchors)
```

### Plots

::: {.rmdnote}

Hover over plot titles for the top words of each topic. Hover over the series to reveal the country.

:::

```{r}
data1 <- summarised_theta_by_month %>%
  filter(anchor %in% c("brexit", "cbdc", "covid", "ukrain"))

plot1 <- ggplot(data1) +
  geom_line_interactive(
    aes(x=date, y=avg_proportion, colour=country, tooltip=country, data_id=country),
    alpha=0.4, show.legend=FALSE
  ) +
  facet_wrap_interactive(
    ~ anchor, ncol=1,
    labeller = labeller_interactive(aes(tooltip=label_top_words[anchor], data_id=anchor))
  ) +
  scale_x_date(breaks = "2 years", date_labels="%Y") +
  labs(x="", y="Averaged topic proportions")

girafe(ggobj = plot1) %>%
  girafe_options(
    opts_hover(css = "stroke-opacity:1;"),
    opts_hover_inv(css = "opacity:0.5;filter:saturate(20%);")
  )
```

```{r}
data2 <- summarised_theta_by_month %>%
  filter(anchor %in% c("polici", "basel", "inflat", "monetary_policy_"))
  
plot2 <- ggplot(data2) +
  geom_line_interactive(
    aes(x=date, y=avg_proportion, colour=country, tooltip=country, data_id=country),
    alpha=0.4, show.legend=FALSE
  ) +
  facet_wrap_interactive(
    ~ anchor, ncol=1,
    labeller = labeller_interactive(aes(tooltip=label_top_words[anchor], data_id=anchor))
  ) +
  scale_x_date(breaks = "2 years", date_labels="%Y") +
  labs(x="", y="Averaged topic proportions")

girafe(ggobj = plot2) %>%
  girafe_options(
    opts_hover(css = "stroke-opacity:1;"),
    opts_hover_inv(css = "opacity:0.5;filter:saturate(20%);")
  )
```
